### 2023-11-08 Scripts/Manuscript/manuscript.Rmd
added the statistics for Hypothesis 1.

INSERT REPLICATION RATIO TABLE HERE

Existing materials were used for 73 of the 77 measures in replications and for 28 in original studies. The specific version of the measure was reported for thirteen measures in replications, and nine measures in original articles. For those measures that were not based on existing materials, one in the replications and twelve in original articles clearly stated that they were newly created for the study. Only one measure in the original articles was modified from its original source during the data collection period, all other measures were modified before that, if at all.

@@

Figure XXX depicts the type of measure (single-item, multiple item, or not a scale), if for the measure reliability was reported or not, and what type of reliability coefficient was reported. Reliabilities were only assessed for multiple item measures, which were approximately equal between replication and original (35 and 38, respectively). Looking at the multiple item measures, four in the replication protocols and twelve in the original articles reported a reliability coefficient. The most commonly reported reliability coefficient was Cronbach's alpha, which accounted for three out of four reported reliabilities in the replication protocols, and eleven out of twelve in the original articles.

@@

A chi-squared test compared whether the number of reliabilities reported among multiple item measures differed between replications and original. Reliabilities were found to be more commonly reported in original articles compared to replication protocols ($\chi^{2}(1) = 4.09, p = 0.043$). These results are contradictory to hypothesis 1.

>>>>

Existing materials were used for `r apa_num(table(coded_data_replications$sel_existing)["True, namely:"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures in replications and for `r apa_num(table(coded_data_original_shortened$sel_existing)["True, namely:"], digits = 0)` in original studies. The specific version of the measure was reported for `r apa_num(length(coded_data_replications$op_version[coded_data_replications$op_version != ""]), numerals = FALSE)` measures in replications, and `r apa_num(length(coded_data_original_shortened$op_version[coded_data_original_shortened$op_version != ""]), numerals = FALSE)` measures in original articles. For those measures that were not based on existing materials, `r apa_num(table(coded_data_replications$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in the replications and `r apa_num(table(coded_data_original_shortened$sel_existing)["False, materials were newly developped for this study"], numerals = FALSE)` in original articles clearly stated that they were newly created for the study. Only `r apa_num(table(coded_data_original_shortened$mod_time)["After/During"], numerals = FALSE)` measure in the original articles was modified from its original source during the data collection period, all other measures were modified before that, if at all.

@@

Figure XXX depicts the type of measure (single-item, multiple item, or not a scale), if for the measure reliability was reported or not, and what type of reliability coefficient was reported. Reliabilities were only assessed for multiple item measures, which were approximately equal between replication and original (`r apa_num(table(coded_data_replications$N_items)["multiple item measure"])` and `r apa_num(table(coded_data_original_shortened$N_items)["multiple item measure"])`, respectively). Looking at the multiple item measures, `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` in the replication protocols and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles reported a reliability coefficient. The most commonly reported reliability coefficient was Cronbach's alpha, which accounted for `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_replications$N_items, coded_data_replications$reliability_type)["multiple item measure", - c(1, 3)]), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", "alpha"]), numerals = FALSE)` out of `r apa_num(sum(table(coded_data_original_shortened$N_items, coded_data_original_shortened$reliability_type)["multiple item measure", - c(1, 3, 4)]), numerals = FALSE)` in the original articles.

@@

A chi-squared test compared whether the number of reliabilities reported among multiple item measures differed between replications and original. Reliabilities were found to be more commonly reported in original articles compared to replication protocols ($\chi^{2}$(`r apa_num(H1_test_result$parameter)`) = `r apa_num(H1_test_result$statistic)`, *p* = `r apa_p(H1_test_result$p.value)`). These results are contradictory to hypothesis 1.
